---
title: "GeoPAT 2"
subtitle: "analysis of spatial and temporal patterns"
author: "Jakub Nowosad"
date: "2018-08-22 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
          css: ["my_theme.css", "default"]
          lib_dir: libs
          nature:
                  highlightStyle: github
                  highlightLines: true
                  countIncrementalSlides: false
                  ratio: 16:9
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

---
layout: false
class: middle, center

## Introduction

---
layout: false
class: middle, center

## Core ideas

---
layout: false
class: middle, center

## Search

---
layout: false
class: middle, center

## Compare

---
layout: false
class: middle, center

## Segmentation

---
layout: false
class: middle, center

## Clustering

---
layout: false
class: middle, center

## Extendibility

---
layout: false
class: middle, center

## Conclusions

---
layout: false
class: reverse, middle, center

```{r, include=FALSE, eval=FALSE}
devtools::install_github("ropenscilabs/icon")
```

## Thank you

.pull-left[
## Me:

Twitter: `r icon::ii_social_twitter()` jakub_nowosad

Email: nowosad.jakub@gmail.com
]

.pull-right[
## Resources:

https://nowosad.github.io

http://sil.uc.edu
]

.footnote[
**Slides:** https://github.com/Nowosad/geostat18
]
